---
title: "Friday Apr 21 Document"
author: "Ben"
date: "2023-04-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Practice with functions in R

Given $h(x) = \sqrt{3-x}$
, we'll compute $h(-4)$ and $f(5)$
 inside an R coding chunk.
 
 Let's define the function first. 

```{r}
h <- function(x){sqrt(3-x)}
```

Now let's compute $h(-4)$ and $h(5)$. 
```{r}
h(-4)
h(5)
```
 
Note that $h(5)$ is not defined, because 3-5 is negative. 

You can actually perform computations inline as well, by typing something like $h(1)=`r h(1)`$.

You can actually refer to things defined in previous code chunks. As an example, we can compute $h(-4)$ in a code chunk, and then refer to it later after having given it a name. 

```{r, echo = FALSE}
value <- h(-4)
```

We obtained $h(-4)=`r value`$.

## Class Practice problems

1. Let's evaluate $w(v) = v^2 - 5v -6$ at a few points, namely $-1,-3,6,4$.

    ```{r}
w <- function(v){v^2 - 5*v -6}
v <- c(-1,3,6,4)
w(v)
    ```

1. Now let's evaluate $f(x) = \frac{2x+4}{x^2}$ at a few points. 

    ```{r}
f <- function(x){(2*x+4)/x^2}
x <- c(-4,1,0)
f(x)
    ```

    The Inf above shows because we tried to divide by zero. 


